\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

% Formatting sections
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

\begin{document}

\pagestyle{empty}

% Header
\begin{center}
    {\Huge \textbf{YOUR NAME}} \\
    \vspace{2mm}
    City, State \textbullet \ (123) 456-7890 \textbullet \ email@example.com \\
    \href{https://linkedin.com/in/yourprofile}{linkedin.com/in/yourprofile} \textbullet \ \href{https://github.com/yourusername}{github.com/yourusername}
\end{center}

% Education
\section{Education}
\textbf{University Name} \hfill City, State \\
\textit{Bachelor of Science in Computer Science} \hfill Month Year -- Month Year \\
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{GPA:} 3.8/4.0
    \item \textbf{Relevant Coursework:} Data Structures \& Algorithms, Operating Systems, Distributed Systems, Machine Learning, Compilers, Database Systems.
\end{itemize}

% Skills
\section{Technical Skills}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Languages:} C++, Java, Python, Dart, JavaScript, SQL, Go
    \item \textbf{Frameworks \& Tools:} Flutter, React, Node.js, Kubernetes, Docker, TensorFlow, Git, AWS/GCP
    \item \textbf{Concepts:} System Design, Object-Oriented Programming, Microservices, CI/CD, RESTful APIs
\end{itemize}

% Experience
\section{Experience}
\textbf{Tech Company Name} \hfill City, State \\
\textit{Software Engineer Intern} \hfill Month Year -- Month Year
\begin{itemize}[noitemsep, leftmargin=*]
    \item Developed a scalable microservice using Go and gRPC to handle 10k+ concurrent requests, reducing system latency by 40\%.
    \item Optimized complex SQL queries in PostgreSQL, resulting in a 25\% reduction in page load times for the internal analytics dashboard.
    \item Collaborated with cross-functional teams to implement a new authentication flow using OAuth 2.0, improving security compliance.
\end{itemize}

\textbf{Startup Name} \hfill City, State \\
\textit{Full Stack Developer} \hfill Month Year -- Month Year
\begin{itemize}[noitemsep, leftmargin=*]
    \item Built and deployed a cross-platform mobile application using Flutter, acquiring 5,000+ users in the first month of launch.
    \item Implemented a real-time chat feature using WebSockets and Redis, ensuring sub-100ms message delivery for active users.
    \item Automated deployment pipelines using GitHub Actions, cutting deployment time from 20 minutes to 5 minutes.
\end{itemize}

% Projects
\section{Projects}
\textbf{Distributed Key-Value Store} \hfill \textit{C++, RPC, Raft Consensus}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Designed and implemented a fault-tolerant key-value store supporting linearizable consistency using the Raft consensus algorithm.
    \item Achieved throughput of 5,000 operations/sec across a 5-node cluster, demonstrating strong understanding of distributed systems.
\end{itemize}

\textbf{AI-Powered Resume Analyzer} \hfill \textit{Python, NLP, Flask}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Developed a web application that parses resumes and matches them against job descriptions using TF-IDF and cosine similarity.
    \item Deployed the application on Google Cloud Platform (GCP) using App Engine and Cloud SQL.
\end{itemize}

\end{document}
